---
title: "Assignment3_stat123"
author: "Koki Itagaki"
date: "2023-03-09"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
#Q1 The commands generate a normal distribution with a mean of 50 and a standard 
deviation of 10.
Create a histogram to show the range of values that covers the middle 95% of
this distribution, using the
title of "Normal Distribution with Mean 50 and SD 10", light blue color, and 
breaks equal to 30.
```{r}
set.seed(123)
data <- rnorm(10000, mean = 50, sd = 10)
hist(data, main ="Normal Distribution with Mean 50 and SD 10", sub = "Written 
by Koki Itagaki",xlab = "Values", ylab = "Frequency",breaks = 30, 
col = "lightblue")

q <- quantile(data, c(0.025, 0.975))
abline(v = q, lty = 2, col = "red")


```
2. Download the data sets sampledata.csv with 100 numeric variables, name it 
mydata and save it to whatever directory you are using for this question.
```{r}
set.seed(123)
mydata<- read.csv("/Users/itagakikouki/stat123/assignment3/sampledata.csv")

head(mydata)
dim(mydata)
#(a) Use a for loop to calculate the mean and standard deviation for each variable in mydata.

means <- numeric(ncol(mydata))
sds <- numeric(ncol(mydata))


for (i in 1:ncol(mydata)) {
  means[i] <- mean(mydata[,i])
  sds[i] <- sd(mydata[,i])
  print(paste("Mean for X ", i," is ", means[i]))
  print(paste0("Standard deviations for X",i," is ", sds[i]))

}

#(b) Use an if statement to identify the variables with a mean greater than 
#10.5 and store their names in a vector 
new_vector <- character()

for (i in 1:ncol(mydata)) {
  if((means[i]) > 10.5){
    new_vecrtor<- c(new_vector, names(mydata)[i])
  }
}
print(new_vecrtor)
```
3. Use the dataset mydata in question 2.
```{r}
set.seed(123)
#(a) Calculate the mean for each variable.
sapply(mydata,mean)
print(is.numeric(unlist(mydata)))
#(b) Calculate the 90% confidence interval for each variable

alpha<-0.1
for(i in 1:ncol(mydata)){
  n <- length(mydata[[i]])
  mean_val <- mean(mydata[[i]])
  sd_val <- sd(mydata[[i]])
  t_val <- qt(1 - alpha / 2, df = n - 1)
  lower_ci <- mean_val - t_val * sd_val / sqrt(n)
  upper_ci <- mean_val + t_val * sd_val / sqrt(n)
  print(paste("90% of confidence interval for variable X",i," is ",round(lower_ci,   2), ", ", round(upper_ci, 2)))
}

  
#(c) Print the results using a matrix with three columns named 
#("Mean", "Lower_CI", and "Upper_CI").
result_matrix <- matrix(NA, nrow = ncol(mydata), ncol = 3, 
                         dimnames = list(names(mydata), c("Mean", "Lower_CI", "Upper_CI")))

for (i in 1:ncol(mydata)) {
  mean_val <- mean(mydata[[i]])
  n <- length(mydata[[i]])
  stder <- sd(mydata[[i]]) / sqrt(n)
  alpha <- 0.1
  t_val <- qt(1 - alpha/2 , df = n - 1)
  lower_ci <- mean_val - t_val * stder/sqrt(n)
  upper_ci <- mean_val + t_val * stder/sqrt(n)
  result_matrix[i, 1] <- mean_val
  result_matrix[i, 2] <- lower_ci
  result_matrix[i, 3] <- upper_ci
}

print(result_matrix)




```
4. Consider the built-in data set UCBAdmissions in R.
```{r}
set.seed(123)
data(UCBAdmissions)

#(a) If we are interested in the proportion of people that apply to Berkeley
#University and get accepted, what is the population of interest and 
#what is the parameter of interest?

#The population of interest is all peoole who apply to Berkeley University
#The parameter of interest is the proportion people who apply to Berkeley 
#University and got accepted.

#(b) Using the command ? UCBAdmissions, determine the variables in the dataset
#and describe what kind of variables they are.
#?UCBAdmissions

#There are 3 variables: Admit, Gender, and Dept.
#First of all, Admit is a categorical variable
#which describes if the applicants got admitted or not. This variable has two levels: Admitted and Rejected 
#Second of all, Gender is a categorical variable which describes genders of applicants. There are two levels:Male and Female
#Lastly, Dept is also categorical variable. Dept shows different departments which applicants applied to. This has 6 levels:A,B,C,D,E,and F.
#(c) Create a variable in R called totalAdmissions which contains the total number of students who were admitted to the university (across all genders and departments).

totalAdmissions <- sum(UCBAdmissions["Admitted", , ])
totalAdmissions
#(d) Create a variable in R called totalRejections which contains the total
#number of students who were rejected to the university (across all genders a
#                                                        nd departments).
totalRejections <- sum(UCBAdmissions["Rejected",,])
totalRejections
#(e) Create a variable in R called totalApplicants which contains the total n
#umber of students who applied to the university in our sample.
totalApplicants <- sum(UCBAdmissions)
totalApplicants

#(f) What is the observed value of the statistic we should use to estimate the population parameter of interest?
pop_prop<- totalAdmissions/totalApplicants
pop_prop
#(g) What is the estimated standard error for ^p?
est_stdError<- sqrt(pop_prop*(1-pop_prop))/totalApplicants
est_stdError
#(h) What is the critical value for a 92% con_dence interval for p?
#1-a = 0.92
#a = 0.08
#a/2 = 0.04 = 96%
cri_p<-qnorm(0.96)
cri_p
#(i) What is the margin of error for our estimate?
est_stdError*cri_p
#(j) Compare that to result of the approximate margin of error formula we
#learned earlier in the course.
app_me<- cri_p*sqrt((pop_prop*(pop_prop))/totalApplicants) 
app_me
#(k) Determine a 92% con_dence interval for the true value of the population proportion
upper<- 0.3877596 + 0.0001884673
lower<-0.3877596 - 0.0001884673
print(paste("The 92% CI is betweeen",lower,"and", upper))
```
#(a) If we are interested in the proportion of people that apply to Berkeley
#University and get accepted, what is the population of interest and 
#what is the parameter of interest?

#The population of interest is all peoole who apply to Berkeley University
#The parameter of interest is the proportion people who apply to Berkeley 
#University and got accepted.

#(b) Using the command ? UCBAdmissions, determine the variables in the dataset
#and describe what kind of variables they are.
#?UCBAdmissions

#There are 3 variables: Admit, Gender, and Dept.
#First of all, Admit is a categorical variable
#which describes if the applicants got admitted or not. This variable has two levels: Admitted and Rejected 
#Second of all, Gender is a categorical variable which describes genders of applicants. There are two levels:Male and Female
#Lastly, Dept is also categorical variable. Dept shows different departments which applicants applied to. This has 6 levels:A,B,C,D,E,and F.


