---
title: "Stat 123 Homework Assignment 1"
author: "Koki Itagaki"
date: "2023-01-26"
output:
  word_document: default
  html_document: default
---

#Q1 Twenty bottles of water were randomly selected from a large collection of bottles in a company's warehouse. These twenty bottles are referred to as the:

a) Parameter
b) Population
c) Sample


Answer) c

#Q2 A journalist wanted to know how his constituents felt about a planned rezoning. He randomly selected 234 names from the city phone directory and conducted a phone survey.

##a) What is the population of interest?
##b) What is the sample of interest?
##c) What type of sampling was used?

Answer:
a)all constituents in the city

b)234 names from the city phone directory

c)simple random sample 



#Q3 You can see a sample of dataset below.
#Patient ID Cancer Type Number of Visits Status
#123_87         Lung        3            Death
#134_99         Brain       4            Survival
#135_46         Breast      5            Death
#124_76         Kidney      3            Death
#132_54         Lung        6            Survival

(a) What are the individuals in the data set?
(b) What are the variables in the data set?
(c) Determine if each variable is categorical or numerical

Answer:
(a)Patient ID

(b)Cancer type, Number of visits, and Status

(c)Cancer type: Categorical variables
   Number of visits: Numerical variables 
   Status: Categorical variables 





#Q4. A journalist is trying to determine the average age of the BC residents who have received fines
#for violating restrictions related to COVID-19. He solicits data from a local police department
#and records the following ages for the five tickets given out by this precinct. #13; 10; 25; 34; 15

```{r}
Sample<- c(13,10,25,34,15)

#(a) What is the parameter of interest?
print("My answer : The average age of the BC residents who have received fines for violating restrictions related to COVID-19")

#(b) Estimate the sample varience. Round your answer to 2 decimal places.
sample_vari<- round(var(Sample),2)
sample_vari

#(c) Estimate the sample mean. Round your answer to 2 decimal places.
x <- mean(Sample)
round_x<-round(x,2)
round_x


```
(a) The average age of the BC residents who have received fines for violating restrictions related to COVID-19




#Q5 Create the following data frame called Sample using the data.frame() function.
##ID Name Age Vote
##1 Juan 22 TRUE
##2 Maria 15 FALSE
##3 Mark 19 TRUE


```{r}
Sample<- data.frame(ID = c(1,2,3), Name = c("Juan", "Maria", "Mark"), Age = c(22,15,19), Vote = c(TRUE,FALSE,TRUE))
Sample
#(a) Create a character vector called Age which contains the values from the second column of the Sample.
Age <- Sample[,2]
Age


#(c) Calculate the number of TRUE votes in the third column.

NumT<- sum(Sample$Vote == TRUE)
NumT
#(d) Calculate the average of the ages in the second column.
Average <- mean(Age)
Average
```



#Q4. Create a list called CourseName and mention the name of courses you have this semester and then create the second list called CourseUnits with the units of each course.

```{r}
CourseName <- list("Stat 123", "Stat 354", "Stat359", "Seng265")
CourseName
CourseUnits <- list(1.5,1.5,1.5,1.5)

#(a) Combine the list CourseName and CourseUnits together.
list<- c(CourseName,CourseUnits)
list

#(b) Change the values of CourseUnits to the character.
CourseUnits<-as.character(CourseUnits)

class(CourseUnits)
```

