---
title: "Assignment2_stat359"
author: "Koki Itagaki"
date: "2023-01-30"
output: html_document
---



#Question 2: A mixture of salt and sucrose was tasted to investigate how
#saltiness was judged depending on sucrose concentration and the
#data are contained in the file: salt.txt
```{r}
salt<-read.table(file ='~/Desktop/stat359/data/salt.txt', sep="",header=TRUE)
salt
saltt<-salt$salt
summary(saltt)
#From the summary function, we can see the mean and the median are different.
#This means the graph is not symmentric.
boxplot(saltt,main= "A mixture of salt and sucrose",sub = 
          "Written by koki Itagaki",col='green',names='salt')
hist(saltt, main = "A mixture of salt and sucrose")
qqnorm(saltt, main = "QQ-plot: A mixture of salt and sucrose")
#From the graphs, we can realize that it is almost symmentric. However, 
#it it slightly different.


#c (b) Estimate the skew (γ1) and kurtosis (γ2) of this distribution 
#using the data. 
skew<-function(x){
  m<-sum((x-mean(x))^3)/length(x)
  s<-sqrt(var(x))^3
  m/s  }
skew.saltt<-skew(saltt)
skew.saltt

kurtosis<-function(x){
  m<- sum(x-mean(x)^4)
  s<-var(x)^4
  m/s -3
}
kur.saltt<-kurtosis(saltt)
kur.saltt
  
#(c) Using the bootstrap construct a 95% confidence interval for the
#population skewness? Does it seem that the population distribution
#generating the data may be skewed? 
x<-saltt ## data for bootstrapping
B<-15000
x.boot<-matrix(data=sample(x=x,size=B*length(x),replace=TRUE),
               nrow=length(x),ncol=B)
skew.boot.sampled<-apply(x.boot,2,skew)
boot.interval<-quantile(skew.boot.sampled,probs=c(0.025,0.975))
boot.interval

hist(skew.boot.sampled, main='Empirical Distribution for salt.txt',xlab='Sampled Values')
abline(v= skew.saltt, col='red')



#(d) Using the bootstrap construct a 95% confidence interval for
#the population kurtosis. Does it seem that the population
#distribution generating the data may have non-zero kurtosis? 



#I use x and B from (c)
x.boot<-matrix(data=sample(x=x,size=B*length(x),replace=TRUE),
               nrow=length(x),ncol=B)
kur.boot.sampled<-apply(x.boot,2,kurtosis)
boot.interval<-quantile(kur.boot.sampled,probs=c(0.025,0.975))
boot.interval

hist(kur.boot.sampled, main='Empirical Distribution for salt.txt',xlab='Sampled Values')
abline(v= skew.saltt, col='red')


```
#(e)Based on your analysis above, what do you conclude about the distribution? 


#Q4. Fusible interlinings are being used with increasing frequency to
#support outer fabrics and improve the shape and drape of various
#pieces of clothing. The data on extensibility (100%) at 100 gm/cm
#for both high quality fabric (H) and poor-quality fabric (P)
#specimens is given in fabric.txt.
```{r}
fab<-read.table(file ='~/Desktop/stat359/data/fabric.txt', sep="",header=TRUE)
fab


#(a) Construct normal qq plots to verify the plausibility of both
#samples having been selected from normal population
#distributions.
#(b) Construct a comparative boxplot. Does it suggest that there is a
#difference between true average extensibility for high-quality
#fabric specimens and that for poor-quality specimens?
```
(c) Decide whether true average extensibility differs for the two
types of fabric. 






