---
title: "hw2_stat123"
author: "Koki Itagaki"
date: "2023-02-13"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
#1. The built-in UCBAdmissions data set is a 3-dimensional array that contains
#the following information:
#• Dimension 1: Admit Admitted, Rejected
#• Dimension 2: Gender Male, Female
#• Dimension 3: Dept A, B, C, D, E, F
#Note: You can find the UCBAdmissions data set using data().
#If you wanted to access the data, you could type in UCBAdmissions[1,1,2] to get
#this value. If you wanted to create a table with the number of rejected 
#students in department A, you could type UCBAdmissions [2, ,1].

```{r}
#(a) Create (and print out) a table that contains all students in department D
UCB<-data(UCBAdmissions)
#Department D is a 4th of the dimention 3. So I just use hard brancket to 
#get all data which students are in the department D
d_data<-UCBAdmissions[, ,4]
d_data
rowSums(UCBAdmissions)

#(b) Create (and print out) a vector called department.D that contains the 
#admitted and rejected students.
department.D<-UCBAdmissions [, ,4]
department.D
#Hint: You may need to use rowSums() on your answer from part (a).

#(c) Create a bar plot displaying the admitted and rejected students in 
#Department D. Make sure to include a main title and label your x-axis. Also, 
#make sure that each bar is a different color.

barplot(department.D,main = "The students in the department D",xlab = "The 
number ofd students",legend = c("Admitted males", "Rejected males", 
"Admitted females","Rejected females"), col = rainbow(4),
sub = "Written by Koki Itagaki",beside = TRUE)

#(d) Create (and print out) a vector called admitted.females which contains
#the admitted females in Department D.
#The number of females is the first row and the secound column.
admitted.females<-UCBAdmissions [1,2 ,4]

admitted.females

#(e) Create (and print out) a vector called pct.admitted.females which contains
#the percentage of admitted females in department D.


pct.admitted.females = round((admitted.females/sum(department.D))*100,
                              digits = 2)
print(paste(pct.admitted.females,"%"))
#(f) Create a pie chart that displays the pct.admitted.females data. 
#Be sure to include a main title for your pie chart.

pct.departmentD = round((department.D/sum(department.D))*100,
                              digits = 2)
pct.departmentD
element_d<- paste(c("Admitted males", "Rejected females", "Admitted females",
                    "Rejected males"),pct.departmentD, "%")
pie(pct.departmentD,labels = element_d ,main = "Pie chart for the department D")



```

#(g) What does the pie chart imply about the number of admitted females 
#in department D?
The pie chart implies that the number of admitted females are the least number
compared to the other categories. Also,we could say there is a trend of that 
more males get admitted compared to females by approximately 1%.
Moreover, most of the people who applied got rejected.
In total, only about 30% of people get admmited.



#2. The following question deals with the data set 
#Government_expenditure_per_student.csv, which you
#will need to download from the assignment page.
```{r}

#(a) Create (but do not print) a vector called expenditure containing the
#last column of the dataset named Value.
Value<-read.csv("/Users/itagakikouki/stat123/Government_expenditure_per_student.csv")
expenditure<-Value[,ncol(Value)]


#(b) Create a histogram displaying the distribution of this variable.
#Be sure to have both a main title and a title on your x-axis.
hist(expenditure, main ="The goverments expenditure per student", 
     xlab = "The amount of expenditure",sub = "Written by Koki Itagaki")

#(c) Describe the shape of the distribution (symmetric, left-skewed, 
#                                           right-skewed).
print("From the histgram above, we can see that the data loooks symmentric.
However, there are a few extra data on the left side of the peak point.
It is possibly right-skewed, but I would say this is symmentric.")


#(d) Compute the appropriate center value and the corresponding measures 
#of variability.

#For the center value, I will find the median.
#I just use the function called median
#To find the mesures of variability, I also get standard deviation by using
#sd function
median(expenditure)
sd(expenditure)
#(e) Remove decimals from the vector named expenditure by using round() and
#create a stem plot
re_expenditure<-round(expenditure,0)
stem(re_expenditure)

```

#(c) Describe the shape of the distribution (symmetric, left-skewed, 
#                                           right-skewed).
From the histgram above, we can see that the data loooks symmentric.
However, there are a few extra data on the left side of the peak point.
It is possibly right-skewed, but I would say this is symmentric.









