---
title: "Lab6_stat123"
author: "Koki Itagaki"
date: "2023-03-01"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



#1. Generate a dataset of student grades, with columns for the student's name, their midterm score, and their final exam score as below.
#name = c("Alice", "Bob", "Charlie", "David", "Emily", "Frank", "Grace",
#"Henry", "Isabel", "John","Karen", "Liam", "Megan", "Nate", "Olivia"),
#midterm = c(80, 70, 91, 85, 55, 80, 95, 50, 65, 75, 80, 85, 90, 75, 80),
#final = c(85, 80, 70, 90, 55, 85, 90, 75, 85, 70, 80, 80, 70, 60, 75)
```{r}
#(a) Take this dataset as input and returns a vector of the final grades for 
#each student. (weighted avetrage of the midterm is(0.4)and final score is 0.6)
data<-data.frame(name = c("Alice", "Bob", "Charlie", "David", "Emily", 
"Frank", "Grace","Henry", "Isabel", "John","Karen", "Liam", "Megan", "Nate",
"Olivia"),
midterm = c(80, 70, 91, 85, 55, 80, 95, 50, 65, 75, 80, 85, 90, 75, 80),
final = c(85, 80, 70, 90, 55, 85, 90, 75, 85, 70, 80, 80, 70, 60, 75))
data

#To get final grades
grades<-data$midterm*0.4 + 0.6*data$final

#(b) Use if statements to assign a letter grade (A, B, C, D, or F) to the 
#student named "Charlie. " (weighted average of the midterm is (o.4) and 
#final scores is (0.6)), with the following criteria:
#A: grade >= 90
#B: grade >= 80 and grade < 90
#C: grade >= 70 and grade < 80
#D: grade >= 60 and grade < 70
#F: grade < 60

letter_grades <- character(1)
letter_grades
if(grades[3]>= 90){
  
}else if(grades[3]>= 90){
  letter_grades<- "A"
}else if(grades[3]>= 80){
  letter_grades<- "B"
}else if(grades[3]>= 70){
  letter_grades<- "C"
}else if(grades[3]>= 60){
  letter_grades<- "D"
}else{
  letter_grades<- "F"
  
}
print(letter_grades)

#Bonus
#create vecttor first
letter_grade<-character(length(grades))
letter_grade<-ifelse(grades >= 90, "A",
              ifelse(grades >= 80, "B",
              ifelse(grades >= 70, "C",
              ifelse(grades >= 60, "D","F"))))
letter_grade
           
#Add new column       
data$grade <-letter_grade 
data
```
#2. You have a variable x that contains a numeric value. You can consider any 
#numeric value for x.
```{r}

#(a) Check whether x is positive, negative, or zero.
x<- -9
if(x>0){
  print("x is positive")
}else if(x<0){
  print("X is negative")
}else{
  print("X is zero")
}

#(b) Considering the numeric value of x, print out x “is positive” or x “is 
#negative” or x “is zero.”


```

#3. Load the normal_distribution.csv dataset and save it as nd. 
```{r}
nd<-read.csv("/Users/itagakikouki/stat123/lab6/normal_distribution.csv")
dim(nd)
head(nd)
nd<-as.numeric(nd$normal)
#(a) Generate the density curve of the nd using the density() function.
hist(nd, main = "The dencity curve of the normal distribution", prob = TRUE,
     col = "lightblue")
#Density function to plot the dencity of the curve
lines(density(nd))
#(b) Find the mean of nd and save it as mu.
mu<- mean(nd)
mu
#(c) find the standard deviation of nd and save it as sig.
sig<-sd(nd)
sig
#(d) Use the function quantile() and the values mu and sig to find the value
#in nd that is greater than 65% of the values in nd. 
quantile(nd, .65)
```

