---
title: "Lab7"
author: "Koki Itagaki"
date: "2023-03-07"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


1. Generate a sequence of random integers between 20 and 30 without replacement, and you want to stop the sequence once a value of 27 is generated. Please use a while loop and an if statement to accomplish this.
```{r}
x<- 0
stop<- FALSE
while(stop == FALSE){
  x<-sample(20:30,1,replace = FALSE)
  print(x)
  if(x == 27){
    stop <- TRUE
  }
  
}
```
2. Write a program that reads in a list of numbers (6, 7, 4, 3, 1, 6, 7, 4, 9).

```{r}
(a) calculate the sum of the even numbers using a “for” loop and “if” condition.
(b) print out "The sum of even numbers is" with the sum of even numbers.


```

3. Download the data set boombust.csv and save it to whatever directory you are using for this course. The goal is to write a for-loop to create a new column at the end of the matrix that contains the sum of each row.
```{r}
(a) Create a matrix that contains only the numerical values and name it nums
(b) Create a new column of zeros at the end of nums by using: nums = cbind(nums, rep(0, length(nums[,1]))).
(c) Write a for-loop that calculates the sum (for each row) of the first through eighth columns of nums and saves the sum in the nineth column of nums. ie.
(d) Print out the nums matrix.
```


```{r}

```
